Crystals

### 2017-01-27 doc/ms.tex
Wrote a tad

\subsection{The shape of the model curve}
The function $f(\x)$, defined from $\x_{\rm min}$ to $\x_{\rm max}$,
is assumed to be a sum of the following components:
\begin{enumerate}
\item A background component
\item $N_{\rm wide}$ wide gaussians
\item $N_{\rm narrow}$ narrow gaussians, to model the spikes
\end{enumerate}

>>>>

\subsection{The shape of the model curve}
The algorithm fits the data with a model curve
$f(\x)$, defined between $\x=\x_{\rm min}$ and $\x=\x_{\rm max}$,
which is assumed to be a sum of the following components:
\begin{enumerate}
\item A background component
\item $N_{\rm wide}$ wide gaussians
\item $N_{\rm narrow}$ narrow gaussians, to model the spikes.
\end{enumerate}

We compute the posterior distribution for the unknown parameters of the
components, and use \citep{dnest4} to generate samples from that posterior
distribution, representing plausible parameter values. From each sample,
it is possible to compute the crystallinity, making it straightforward to
calculate the marginal posterior distribution of the crystallinity, describing
uncertainty about its value in the light of the data.
